---
title: "Topic 2"
output:
  word_document: default
  html_document: default
---



```{r cars}
library(reshape2)
library(tidyverse)
library(ggplot2)
library(dplyr) 
library(RColorBrewer)
```

## Reading the RADAR data set.

```{r pressure, echo=FALSE}
dapp<- read.csv("radar.csv")
```

## Data Preprocessing
```{r}
for(i in 1:length(dapp$Txs_24h)){
  if(grepl('[.,]',dapp$Txs_24h[i])){
    dapp$Txs_24h[i]<-  gsub('[.,]', '', dapp$Txs_24h[i])
    dapp$Txs_24h[i]<-  gsub('[k,]', '00', dapp$Txs_24h[i])
    dapp$Txs_24h[i]<-  gsub('[M,]', '00000', dapp$Txs_24h[i])
  }
  else{
    dapp$Txs_24h[i]<-  gsub('[k,]', '000', dapp$Txs_24h[i])
    dapp$Txs_24h[i]<-  gsub('[M,]', '000000', dapp$Txs_24h[i])
  }

}
dapp$Txs_24h<-as.numeric(dapp$Txs_24h)

for(i in 1:length(dapp$Txs_7d)){
  if(grepl('[.,]',dapp$Txs_7d[i])){
    dapp$Txs_7d[i]<-  gsub('[.,]', '', dapp$Txs_7d[i])
    dapp$Txs_7d[i]<-  gsub('[k,]', '00', dapp$Txs_7d[i])
    dapp$Txs_7d[i]<-  gsub('[M,]', '00000', dapp$Txs_7d[i])
  }
  else{
    dapp$Txs_7d[i]<-  gsub('[k,]', '000', dapp$Txs_7d[i])
    dapp$Txs_7d[i]<-  gsub('[M,]', '000000', dapp$Txs_7d[i])
  }
  
}

dapp$Txs_7d<-as.numeric(dapp$Txs_7d)
median(dapp$Txs_7d)


for(i in 1:length(dapp$balance)){
  if(grepl('[.,]',dapp$balance[i])){
    dapp$balance[i]<-  gsub('[.,]', '', dapp$balance[i])
    dapp$balance[i]<-  gsub('[k,]', '00', dapp$balance[i])
    dapp$balance[i]<-  gsub('[M,]', '00000', dapp$balance[i])
  }
  else{
    dapp$balance[i]<-  gsub('[k,]', '000', dapp$balance[i])
    dapp$balance[i]<-  gsub('[M,]', '000000', dapp$balance[i])
  }
  
}

dapp$balance<-as.numeric(dapp$balance)
summary(dapp$balance)


for(i in 1:length(dapp$volume_24h)){
  if(grepl('[.,]',dapp$volume_24h[i])){
    dapp$volume_24h[i]<-  gsub('[.,]', '', dapp$volume_24h[i])
    dapp$volume_24h[i]<-  gsub('[k,]', '00', dapp$volume_24h[i])
    dapp$volume_24h[i]<-  gsub('[M,]', '00000', dapp$volume_24h[i])
    dapp$volume_24h[i]<-  gsub('[$,]', '', dapp$volume_24h[i])
  }
  else{
    dapp$volume_24h[i]<-  gsub('[k,]', '000', dapp$volume_24h[i])
    dapp$volume_24h[i]<-  gsub('[M,]', '000000', dapp$volume_24h[i])
    dapp$volume_24h[i]<-  gsub('[$,]', '', dapp$volume_24h[i])
  }
  
}

dapp$volume_24h<-as.numeric(dapp$volume_24h)
summary(dapp$volume_24h)

for(i in 1:length(dapp$volume_7d)){
  if(grepl('[.,]',dapp$volume_7d[i])){
    dapp$volume_7d[i]<-  gsub('[.,]', '', dapp$volume_7d[i])
    dapp$volume_7d[i]<-  gsub('[k,]', '00', dapp$volume_7d[i])
    dapp$volume_7d[i]<-  gsub('[M,]', '00000', dapp$volume_7d[i])
    dapp$volume_7d[i]<-  gsub('[$,]', '', dapp$volume_7d[i])
  }
  else{
    dapp$volume_7d[i]<-  gsub('[k,]', '000', dapp$volume_7d[i])
    dapp$volume_7d[i]<-  gsub('[M,]', '000000', dapp$volume_7d[i])
    dapp$volume_7d[i]<-  gsub('[$,]', '', dapp$volume_7d[i])
  }
  
}
dapp$volume_7d<-as.numeric(dapp$volume_7d)
summary(dapp$volume_7d)

for(i in 1:length(dapp$users_24h)){
  if(grepl('[.,]',dapp$users_24h[i])){
    dapp$users_24h[i]<-  gsub('[.,]', '', dapp$users_24h[i])
    dapp$users_24h[i]<-  gsub('[k,]', '00', dapp$users_24h[i])
    dapp$users_24h[i]<-  gsub('[M,]', '00000', dapp$users_24h[i])

  }
  else{
    dapp$users_24h[i]<-  gsub('[k,]', '000', dapp$users_24h[i])
    dapp$users_24h[i]<-  gsub('[M,]', '000000', dapp$users_24h[i])
   
  }
  
}
dapp$users_24h<-as.numeric(dapp$users_24h)
summary(dapp$users_24h)
```
## Correlation matrix with rank as target variable
```{r}
features <- c("Txs_24h","Txs_7d", "balance", "volume_24h", "volume_7d","users_24h")
cormat <- round(cor(dapp[c("rank", features)]), 2)

melted_cormat <- melt(cormat)
ggplot(data = melted_cormat, aes(Var2, Var1, fill = value))+
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="Pearson\nCorrelation") +
  theme_minimal()+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                   size = 12, hjust = 1))+
  coord_fixed()
cormat

```
## Reading the STATE OF THE DAPP dataset

```{r}
state_of_dapp<-read.csv("state_of_the_dapp.csv")
state<-state_of_dapp%>%
  arrange(rank)
```

## Data preprocessing

```{r}
for(i in 1:length(state$volume_7d)){
  if(grepl('[USD,]',state$volume_7d[i])){
    state$volume_7d[i]<-  gsub('[USD,]', '', state$volume_7d[i])

  }
  
}
state$volume_7d<-as.numeric(state$volume_7d)
class(state$volume_7d)
state$dev_activity_30d<-as.numeric(state$dev_activity_30d)
```

# Most popular plaforms for Dapp construction
```{r}
state %>% group_by(state$platform, state$status) %>% 
  summarise(Platform=unique(platform), Status=unique(status),n=n()) %>% filter(n>15) %>% 
  ggplot(aes(x=Platform, y=n, fill=Status, label=n))+ geom_col()+ 
  geom_text(size = 2, position = position_stack(vjust = 0.5), color="White") + 
  theme_classic() + labs(title="Most popular platforms for Dapps construction", x="Platform",     y="Dapps count", subtitle = "Source : State_of_the_Dapp")

```
# Ethereum Dapps by Category
```{r}
state %>% filter(platform == "Ethereum") %>%
  group_by(category) %>% summarise(c = unique(category), n=n()) %>%
  ggplot(aes(c,n,label=n, fill=category))+geom_col()+coord_flip()+
  geom_text(size = 2, position = position_stack(vjust = 0.5), color="black") +
  theme_classic()+
  theme(legend.position = "none", panel.background = element_rect(inherit.blank = TRUE)) + 
  labs(title = "Ethereum Dapps by Category", y="Dapps Count", x="Dapps Category", subtitle = "Source : State_of_the_Dapp")

```

# Dapp Loss by category
```{r}
state %>% filter(dapp_total_loss != -1.0000000000) %>% 
  group_by(category) %>% summarise(c = unique(category),n = mean(dapp_total_loss)) %>% 
  filter(n <0) %>% 
  ggplot(aes(c,n,label=round(n), fill="red"))+ geom_col()+ coord_flip()+ 
  geom_text(size = 4, position = position_stack(vjust = 0.5), color="white") +            theme_classic()+
  theme(legend.position="none") + labs(y="Loss of Dapps in USD",title ="Top Category based on Dapps Loss", x="Dapps Category", subtitle = "Source : State_of_the_Dapp")

```
# Dapps profit category
```{r}

state %>% filter(dapp_total_loss != -1.0000000000) %>% 
  group_by(category) %>% summarise(c = unique(category),n = mean(dapp_total_loss)) %>% 
  filter(n >200) %>% 
  ggplot(aes(c,n,label=round(n), fill=c))+ geom_col()+ coord_flip()+ 
  geom_text(size = 3, position = position_stack(vjust = 0.5), color="white") +            theme_classic()+
  theme(legend.position="none") + labs(y="Profit of Dapps in USD",title ="Top Category based on Dapps Profit", x="Dapps Category", subtitle = "Source : State_of_the_Dapp")
```

# Top Category based on transaction count
```{r}

state %>% filter(transaction_count != -1.0000000000) %>% 
  group_by(category) %>% summarise(c = unique(category),n = mean(transaction_count)) %>%
  filter(n>1000) %>% 
  ggplot(aes(c,n,label=round(n), fill=category))+ geom_col()+ coord_flip()+ 
  geom_text(size = 2, position = position_stack(vjust = 0.5), color="Black") +            theme_classic()+
  theme(legend.position="none") + labs(y="Average transaction count",title ="Top Category based on transaction count", x="Dapps Category", subtitle = "Source : State_of_the_Dapp")

```

# Top Category based on transaction count
```{r}

state %>% filter(contract_count != -1) %>% 
  group_by(category) %>% summarise(c = unique(category),n = sum(contract_count)) %>%
  ggplot(aes(c,n,label=round(n), fill=category))+ geom_col()+ coord_flip()+ 
  geom_text(size = 2, position = position_stack(vjust = 0.5), color="Black") +            theme_classic()+
  theme(legend.position="none") + labs(y="Total contract count",title ="Top Category based on contract count", x="Dapps Category", subtitle = "Source : State_of_the_Dapp")

```


# Top category based on 7 days volume.
```{r}
state %>% filter(!(volume_7d == 0)) %>% 
  group_by(category) %>% summarise(c = unique(category),n = mean(volume_7d)) %>% filter(n>100000) %>% 
  ggplot(aes(c,n,label=round(n), fill=category))+ geom_col()+  
  geom_text(size = 3, position = position_stack(vjust = 0.5), color="Black") +                theme_classic()+
  theme(legend.position="none") + labs(y="Average volume in USD ",
  title ="Top Category based on 7 days volume", x="Dapps Category", subtitle = "Source : State_of_the_Dapp")
```



## Correlation matrix for state of the dapp dataset
```{r}
state$users_24h<-as.numeric(state$users_24h)
features <- c("dev_activity_30d","transaction_count", "total_transaction_volume_ether", "volume_7d","users_24h","contract_count","dapp_total_loss","user_loss_average")
cormat <- round(cor(state[c("rank", features)],use="complete.obs"), 2)

melted_cormat <- melt(cormat)
ggplot(data = melted_cormat, aes(Var2, Var1, fill = value))+
  geom_tile(color = "white")+
  scale_fill_gradient2(low = "blue", high = "red", mid = "white", 
                       midpoint = 0, limit = c(-1,1), space = "Lab", 
                       name="Pearson\nCorrelation") +
  theme_minimal()+ 
  theme(axis.text.x = element_text(angle = 45, vjust = 1, 
                                   size = 12, hjust = 1))+
  coord_fixed()
cormat

```

## Regression models to predict rank
```{r}
dapp_filter_zero<-dapp%>%
  filter(users_24h>0)%>%
  filter(Txs_24h>0)%>%
  filter(volume_24h>0)%>%
  filter(balance>0)

plot(lm(data=dapp_filter_zero, rank~volume_24h+Txs_24h+balance))
summary(lm(data=dapp_filter_zero, rank~volume_24h+Txs_24h+balance))
plot(lm(data=dapp_filter_zero, rank~poly(volume_24h, degree=2)+poly(Txs_24h, degree=2)+poly(balance, degree=2)))
summary(lm(data=dapp_filter_zero, rank~poly(volume_24h, degree=2)+poly(Txs_24h, degree=2)+poly(balance, degree=2)))
```

## Regression models to predict Dapp profits
```{r}
state<- state%>%
  filter(dapp_total_loss!=(-1.0000))%>%
  filter(user_total_loss!=(-1.0000))%>%
  filter(user_loss_average!=(-1.0000))%>%
  filter(total_transaction_volume_ether!=(-1.0000))

summary(lm(data= state, dapp_total_loss~total_transaction_volume_ether+user_loss_average+user_count_unique_remove_contract_creator))
plot(lm(data= state, dapp_total_loss~total_transaction_volume_ether+user_loss_average+user_count_unique_remove_contract_creator))
summary(lm(data= state, dapp_total_loss~poly(total_transaction_volume_ether, degree=2)+ poly(user_loss_average, degree=2)+poly(user_count_unique_remove_contract_creator, degree=2)))
plot(lm(data= state, dapp_total_loss~poly(total_transaction_volume_ether, degree=2)+ poly(user_loss_average, degree=2)+poly(user_count_unique_remove_contract_creator, degree=2)))

```

# Top 5 Dapps by rank on radar.
```{r}
dapp %>% 
  filter(rank < 6) %>% summarise(rank=rank,category, Protocol = protocol) %>%
  ggplot(aes(category,rank, col=Protocol))+geom_point(size=4) +
  theme_classic() + labs(title= "Top 5 Dapps based on rank on radar", y="Rank", x="Dapps category", subtitle = "Source : State_of_the_Dapp")
```



















